\thesistitle

### 2019-06-13 main.tex
Literal/variable variability
Trying to explain something
Writing something about Compare

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{titlepic}
\usepackage{vhistory}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage[backend=biber, style=ieee,citestyle=numeric-comp]{biblatex}
\usepackage[colorinlistoftodos, prependcaption]{todonotes}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage[acronym,nogroupskip,nohypertypes={acronym},toc,section=chapter]{glossaries}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{cmap}
\usepackage{float}
\usepackage{hyperref}
\usepackage{wrapfig}

\usepackage{listings}
\lstset{
tabsize = 4, %% Sets tab space width.
showstringspaces = false, %% Prevents space marking in strings, string is defined as the text that is generally printed directly to the console.
numbers = left, %% Displays line numbers on the left.
commentstyle = \color{green}, %% Sets comment color.
keywordstyle = \color{blue}, %% Sets  keyword color.
stringstyle = \color{red}, %% Sets  string color.
rulecolor = \color{black}, %% Sets frame color to avoid being affected by text color.
basicstyle = \small \ttfamily , %% Sets listing font and size.
breaklines = true, %% Enables line breaking.
numberstyle = \tiny,
}

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{titlepic}
\usepackage{vhistory}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage[backend=bibtex, style=ieee,citestyle=numeric-comp]{biblatex}
\usepackage[colorinlistoftodos, prependcaption]{todonotes}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage[acronym,nogroupskip,nohypertypes={acronym},toc,section=chapter]{glossaries}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{cmap}
\usepackage{float}
\usepackage{hyperref}
\usepackage{wrapfig}
\usepackage{microtype}

\usepackage{titlesec}

\setcounter{secnumdepth}{4}

### 2019-06-13 sections/research.tex
Writing something about Compare

\subsubsection{Generating the clone grid}\label{sec:clonegrid}
First of all, we parse the AST obtained from JavaParser into what we call a clone grid. Although it is not a grid in an original sense, thinking of it as a grid makes it easier to comprehend. We have chosen to base our clone detection around statements as the smallest unit of comparison. This means that a single statement cloned with another single statement is the smallest clone we can find. The rationale for this lies in both simplicity and performance efficiency. This means we won't be able to find when a single expression matches another expression, or even a single token matching another token. This is in most cases not a problem, as expressions are often small and do not span the minimal size to be considered a clone in the first place (more about this in section \ref{sec:thresholds}).

@@

\subsubsection{Comparing Statements/Declarations}
In the previous section we described ...

@@

Using the example shown in figure \ref{fig:clonegrid} we can explain how we detect clones. Suppose we are finding clones for two files and the final node of the second file is a variable declarator. This final node is represented in the example figure by the purple box (1). We then follow all ``duplicate'' relations until we have found all clones (2 and 3). We now have a single statement clone class of three clone instances (1, 2 and 3). Next, we move to the previous line (4). Here again, we collect all duplicates of this node (4 and 5). For each of these duplicates, we check whether the node following it is already in the clone class we collected in the previous iteration. In this case, (2) follows (5) and (1) follows (4). This means that node (3) does not form a 'chain' with other cloned statements. Because of this, the clone class of (1, 2 and 3) comes to an end. It will be checked against the thresholds, and if adhering to the threshold, considered a clone. We then go further to yet the previous node (6). In this case, this node does not have any clones. This means we check the (2 and 5, 1 and 4) clone class against the thresholds, and if it adheres, consider it a clone. Dependent on the thresholds, we'd now have found two clone classes.

>>>>

\subsubsection{Generating the clone grid}\label{sec:clonegrid}
First of all, we parse the AST obtained from JavaParser into what we call a clone grid. Although it is not a grid in an original sense, thinking of it as a grid makes it easier to comprehend (this is explained in section \ref{sec:detectingclones} in more detail). We have chosen to base our clone detection around statements as the smallest unit of comparison. This means that a single statement cloned with another single statement is the smallest clone we can find. The rationale for this lies in both simplicity and performance efficiency. This means we won't be able to find when a single expression matches another expression, or even a single token matching another token. This is in most cases not a problem, as expressions are often small and do not span the minimal size to be considered a clone in the first place (more about this in section \ref{sec:thresholds}).

@@

\subsubsection{Comparing Statements/Declarations}
In the previous section we described a ``duplicate'' relation between nodes in the clone grid built by CloneRefactor. Whether two nodes in this grid are duplicates of each other is dependent on the clone type. In this section, we will describe for each type how we compare statements and declarations assess whether they are clones of each other.

CloneRefactor detects six different types of clones: T1, T2, T3, T1R, T2R and T3R. These types are further explained in chapter \ref{chap:clonetypes}. Type 1 clones are an exact textual match between two clones, omitting comments and whitespace. For type 1 clones, CloneRefactor filters the tokens of a node to exclude its comments, whitespace and end of line (EOL) characters and then compares these tokens. For type 2 clones, the tokens are further filtered to omit all identifiers and literals. Type 3 clones do the same node comparison as type 2 clones.

For type 1R clones, this comparison is a bit more advanced. For method calls

@@

Using the example shown in figure \ref{fig:clonegrid} we can explain how we detect clones. Suppose we are finding clones for two files and the final node of the second file is a variable declarator. This final node is represented in the example figure by the purple box (1). We then follow all ``duplicate'' relations until we have found all clones (2 and 3). We now have a single statement clone class of three clone instances (1, 2 and 3). Next, we move to the previous line (4). Here again, we collect all duplicates of this node (4 and 5). For each of these duplicates, we check whether the node following it is already in the clone class we collected in the previous iteration. In this case, (2) follows (5) and (1) follows (4). This means that node (3) does not form a `chain' with other cloned statements. Because of this, the clone class of (1, 2 and 3) comes to an end. It will be checked against the thresholds, and if adhering to the threshold, considered a clone. We then go further to yet the previous node (6). In this case, this node does not have any clones. This means we check the (2 and 5, 1 and 4) clone class against the thresholds, and if it adheres, consider it a clone. Dependent on the thresholds, we'd now have found two clone classes.
